
# EXHIBITS

```{r exhibits_setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
                      fig.align="center", fig.width=6.2, fig.height=2.25, dpi=300)
library(dplyr)
library(ggplot2)
library(scales)
theme_set(theme_bw(base_size = 11))
paper_theme <- theme(
  plot.title = element_text(size = 12, face = "bold", hjust = 0),
  axis.title = element_text(size = 11),
  axis.text  = element_text(size = 10),
  plot.margin = margin(5.5, 12, 5.5, 70, "pt")  # <- fixed left margin
)
```

```{r load_mto_exhibits, include=FALSE}
library(haven)
mto <- read_dta("mto.dta")
```


```{r exA1, echo=FALSE, message=FALSE, warning=FALSE}

df <- mto %>%
  mutate(Group = if_else(voucher == 1, "Voucher offer", "Control")) %>%
  group_by(Group) %>%
  summarize(
    n = n(),
    mean = mean(moved, na.rm = TRUE),
    se = sqrt(mean * (1 - mean) / n),
    lo = pmax(0, mean - 1.96 * se),
    hi = pmin(1, mean + 1.96 * se),
    label = percent(mean, accuracy = 1),
    .groups = "drop"
  )

ggplot(df, aes(x = Group, y = mean)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.15) +
  geom_text(aes(label = label), vjust = -0.6, size = 4) +
  scale_y_continuous(
    limits = c(0, 1),
    breaks = c(0, 0.25, 0.5, 0.75, 1),
    labels = percent_format(accuracy = 1)
  ) +
  labs(x = NULL, y = "Moved (percent)", title = "Exhibit 1. Compliance (First Stage)") +
  theme_bw(base_size = 11) + paper_theme
```

>*Exhibit 1 notes:* Voucher assignment increases moving by \textbf{43.1 percentage points} (control-group moving is essentially zero), indicating one-sided noncompliance and a strong first stage. Whiskers show 95\% confidence intervals for group means.


\vspace{8pt}

```{r exA2, echo=FALSE, message=FALSE, warning=FALSE}

df <- mto %>%
  mutate(Group = if_else(voucher == 1, "Voucher offer", "Control")) %>%
  group_by(Group) %>%
  summarize(
    n = sum(!is.na(kessler)),
    mean = mean(kessler, na.rm = TRUE),
    sd = sd(kessler, na.rm = TRUE),
    se = sd / sqrt(n),
    lo = mean - 1.96 * se,
    hi = mean + 1.96 * se,
    label = round(mean, 2),
    .groups = "drop"
  )

ggplot(df, aes(x = Group, y = mean)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.15) +
  geom_text(aes(label = label), vjust = -0.6, size = 4) +
  scale_y_continuous(
    limits = c(0, 8),
    breaks = c(0, 2, 4, 6, 8)
  ) +
  labs(x = NULL, y = "Mean Kessler score", title = "Exhibit 2. Outcome (ITT)") +
  theme_bw(base_size = 11) + paper_theme
```

>*Exhibit 2 notes:* Mean Kessler distress is lower in the voucher-offer group than in control. This difference corresponds to the ITT estimate (**-0.588** Kessler points). Whiskers show 95% confidence intervals for group means.

```{r exA3}
# compute ITT and first stage (OLS coefficients)
kess_reg <- lm(kessler ~ voucher, data = mto)
move_reg <- lm(moved ~ voucher, data = mto)

ITT_y <- coef(kess_reg)[["voucher"]]
FS    <- coef(move_reg)[["voucher"]]
TOT   <- ITT_y / FS

k0 <- mean(mto$kessler[mto$voucher == 0], na.rm = TRUE)
k_complier_if_moved <- k0 + TOT

df3 <- data.frame(
  Group = c("Control mean", "Complier mean if moved\n(TOT/LATE-implied)"),
  mean = c(k0, k_complier_if_moved),
  label = round(c(k0, k_complier_if_moved), 2)
)

ggplot(df3, aes(x = Group, y = mean)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = label), vjust = -0.6, size = 4) +
  scale_y_continuous(limits = c(0, 8), breaks = c(0, 2, 4, 6, 8)) +
  labs(x = NULL, y = "Mean Kessler score", title = "Exhibit 3. TOT/LATE Illustration") +
  theme_bw(base_size = 11) + paper_theme
```

>*Exhibit 3 notes:* The “Complier mean if moved” bar is not an observed group mean. It is a counterfactual mean implied by the TOT/LATE estimate: starting from the control-group mean Kessler score, we add the TOT/LATE effect (ITT divided by the first stage) to illustrate the magnitude of the implied effect for induced movers.